% Preamble
\documentclass{article}
\setlength\parindent{0pt}

% Packages
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage[linktocpage]{hyperref}

\hypersetup{
    colorlinks   = true,
    urlcolor     = blue,
    linkcolor    = blue,
    citecolor   = red
}

\title{\textbf{ScreenView Protocol}}
\author{Josh Brown}

% Document
\begin{document}
    \maketitle

    \begin{abstract}
        ScreenView is suite of cryptographical and application level networking protocols culminating to create a
        zero configuration end to end encrypted remote screen viewing and controlling software. ScreenView aims to
        replace TeamViewer, RDP, and VNC for many use cases while being more performant and more secure. ScreenView
        requires little setup an is just as easy or easier than other solutions. ScreenView defines four different
        layers of protocols, each encapsulating all the layers below it. Cryptography for communication between peers
        and the server is based upon TLS 1.3 and Wireguard. End-to-end cryptography used for ALL communication between
        peers is based upon TLS-SRP. ScreenView end-to-end cryptography prevents man-in-the-middle attacks even if
        the intermediary server is compromised, unlike TeamViewer. Screen data is sent over UDP to achieve superior
        performance than TCP based solutions such as VNC. All UDP packets must be authenticated with keys established
        over TCP before a response is made by the server preventing amplification attacks. A congestion control
        mechanism is used to handle low bandwidth and poor networking conditions. Finally, ScreenView supports
        advanced use cases including file transfer, multiple displays, sharing specific windows, shared whiteboards,
        and clipboard transfer.
    \end{abstract}

    \newpage

    \tableofcontents
    \newpage


    \section{Definitions}

    The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL NOT",
    "SHOULD", "SHOULD NOT", "RECOMMENDED", "MAY", and "OPTIONAL" in this
    document are to be interpreted as described in \href{https://datatracker.ietf.org/doc/html/rfc2119}{RFC 2119}.

    \newpage

    \input{introduction.tex}

    \input{server-encryption-layer.tex}

    \input{SVSC.tex}

    \input{WPSKKA.tex}

    \input{RVD.tex}

\end{document}
